---
title: "Mean Squared Error for a Weibull baseline intensity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mean Squared Error for a Weibull baseline intensity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::load_all()
library(survival)
```

```{r simulate_linear_data, eval=T}
N <- 50

# true values
lambda01 <- 4
lambda02 <- 1
lambda12 <- 0.5
theta01 <- log(0.4)
theta02 <- log(0.4)
theta12 <- log(1)

# true survivor function
logS_t <- \(t,z) {
  -(lambda01*exp(z*theta01) + lambda02*exp(z*theta02))*t
}

No_visits <- 8

mse <- matrix(nrow=N,ncol=2)
colnames(mse) <- c("Illness-death", "Crude PFS")
set.seed(123)
for (i in 1:N) {
  dat <- sim_exp(N = 300,
                 lambda01,
                 lambda02,
                 lambda12,
                 theta01,
                 theta02,
                 theta12,
                 K = No_visits)
  
  # get KM error
  km <- survfit(Surv(PFSDY, PFS) ~ ATRTN, data=dat)
  km_resid <- exp(logS_t(km$time, c(rep(0,km$strata[1]),rep(1,km$strata[2])))) - km$surv
  
  fit <- weib.fit(dat,method = "Nelder-Mead")
  fns <- do.call(weib.fnBuilder,as.list(fit$par))
  
  fitted <- fns$P00(0, dat$PFSDY, dat$ATRTN)
  resid <-  exp(logS_t(dat$PFSDY, dat$ATRTN)) - fitted
  mse[i,] <- c(mean(resid^2),mean(km_resid^2)) 
}
mse_weib_exp <- mse
```

```{r plot_linear_density}
plot(density(mse_weib_exp[,1]))
lines(density(mse_weib_exp[,2]), col="red")
```
  # get KM error
  km <- survfit(Surv(PFSDY, PFS) ~ ATRTN, data=dat)
  km_resid <- logS_t(km$time, c(rep(0,km$strata[1]),rep(1,km$strata[2])))
  
  # using default initial values of lambda=gamma=1, theta=0
  fit <- weib.fit(dat)
  fns <- do.call(weib.fnBuilder,as.list(fit$par))
  
  fitted <- fns$logP00(0, dat$PFSDY, dat$ATRTN)
  resid <-  logS_t(dat$PFSDY, dat$ATRTN) - fitted
  mse[i,] <- c(mean(resid^2),mean(km_resid^2)) 
}
```

```{r plot_density}
plot(density(mse[,1]), xlim=c(0,1))
lines(density(mse[,2]), col="red")
```
